To Do List

### 2020-09-28 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
Small edits

@@

Mikhail Dozmorov, Ph.D., Blick scholar  
Assistant Professor,  Department of Biostatistics 
Affiliate, Department of Pathology  
Virginia Commonwealth University  
One Capitol Square, room 738  
830 East Main Street  
Richmond,  Virginia  23298  
e-mail:  mikhail.dozmorov@vcuhealth.org  
Phone: 804-827-2055

>>>>

- We provide genomic coordinates of the predicted TAD/loop boundaries for GM12878 and K562 cell lines.

@@

Mikhail Dozmorov, Ph.D., Blick scholar  
Associate Professor,  Department of Biostatistics 
Affiliate, Department of Pathology  
Virginia Commonwealth University  
One Capitol Square, room 738  
830 East Main Street  
Richmond,  Virginia  23298  
e-mail:  mikhail.dozmorov@vcuhealth.org  
Phone: 804-827-2055
